Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-01 sections/04-application.tex
Update on Overleaf.

During the COVID-19 pandemic, the need for reliable and timely nowcasts of the pandemic's development has become apparent.
In Germany, the seven-day hospitalization rate was established as a central steering measure for COVID-19 measures in November 2021, and the imposition of severe public restrictions was based on it~\parencite{RobertKochInstitute2021}.
The Robert Koch Institute (RKI) provides daily reports on the number of new hospitalizations.
However, these reports are subject to delays and revisions in two sources.
The first source is technical delays in the reporting process, for example, due to different authorities passing the data to the RKI~\parencite{RobertKochInstitute2024}.
The second, more systematic source is the structure of the seven-day hospitalization rate.
To a given date, all the cases are allocated whose first positive test result was on that date and who were hospitalized in relation to the disease in the following.
The seven-day hospitalization rate is the average count of cases per $100,000$ inhabitants on the given date and six days before.
Thus, the final seven-day hospitalization rate can only be reported with a significant delay of up to more than 70 days.
Nevertheless, as the seven-day hospitalization rate was considered a major indicator of the pandemic's development, many organizations and institutions started to issue nowcasts, including research teams and newspapers.
To collect nowcasts of the seven-day hospitalization rate by different nowcast groups, the COVID19-Nowcasting-Hub was established~\parencite{ChairOfEconometricsAndStatisticsAtKarlsruheInstituteOfTechnology2024}.
The nowcasts contain the seven-day hospitalization rate's predictive mean, median, and quantiles.

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics{plots/covid_nowcast/00_true_data.pdf}
    \caption{Realisations.}
    \label{fig:app-covid-true}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics{plots/covid_nowcast/00_nowcast_data.pdf}
    \caption{Same-day nowcasts}
    \label{fig:app-covid-nowcast}
        \end{subfigure}
    \caption{True and nowcast data of the seven-day-hospitalization in Germany from November 22, 2021, to April 29, 2022 \parencite{ChairOfEconometricsAndStatisticsAtKarlsruheInstituteOfTechnology2024}.
    The outliers in the RKI model of values above $10^8$ are removed before the following analysis.}
    \label{fig:app-covid-true-nowcast}
\end{figure}

The data contains eight nowcasts from scientific and public institutions, nowcast communities, and a newspaper, using different input variables, calendar data, and length of training data.
The model structures are diverse, including Bayesian models, generalized additive models, and parametric bootstrapping.
Table~\ref{tab:app-covid-models} in the appendix lists the different abbreviations and the model's overall structure.
Using the nowcasts, two ensemble methods are constructed using the ensembles' mean or median.
We denote them by ENS-MEAN and ENS-MED.
In line with the initial study design, we consider the period from November 22, 2021, to April 29, 2022, as the evaluation period.
In contrast to~\textcite{Wolffram2023}, we use the newest data available on the true values, not the data from August 8, 2022.
\unsure{Nochmal längere Evaluation?}
We do not expand on the models' performance on specific regions or age groups in Germany and the probabilistic nowcast assessment.
Figure~\ref{fig:app-covid-true-nowcast} displays the true and nowcast data for the evaluation period.
The time comprises the fourth wave's end in December 2021 and nearly the entire fifth wave of the pandemic in Germany, lasting until May 28, 2022~\parencite{Tolksdorf2022}.
Table~\ref{tab:app-covid-rmse} summarizes the point evaluation measures for the issued mean of the different models.
The models issue same-day nowcasts for nearly all 159 days of the evaluation period~\parencite[see][Tables A2, A3, and A4]{Wolffram2023}.
The best-performing models in terms of RMSE and MAE are the ILM and RKI models.
The ensemble methods perform worse than the best models regarding the mean location.
The performance of the models is diverse, with more than twice as high RMSE values for the worst models compared to the best models.
Note that the high values for the EPI model could be driven by an exceptionally far-off value at the end of the evaluation period.

@@

@@

For some patients, the data includes \ac{abp} and \ac{nbp} measurements.
For an overview of blood pressure measurement methods, see \textcite{Saugel2014}.
While non-invasive blood pressure measurement methods are relatively gentle, they are less accurate than invasive methods.
For critical patients, changes in blood pressure can be crucial for the treatment.
Thus, trending assessment can be performed in addition to standard accuracy analysis~\parencite[see, e.g., ]{Mostafa2020}.
Thus, we assess the trending ability of the non-invasive blood pressure measurements compared to the invasive blood pressure measurements.
Of the 64,168 numerical data records in the database, 2,662 include at least one measurement of systolic \ac{abp} and \ac{nbp} and ... include at least measurements of \ac{abp} and \ac{nbp} at the same time.
The data records generally include measurements for one patient.

@@

Again, we exclude the 10\% of absolute differences in trending assessment.
The resulting four-quadrant plots of the mean and systolic blood pressure measurements for the different lags are shown in Figure~\ref{fig:app-mimic-4q}.
The number of points in the four-quadrant plot is smaller due to the restriction to data records with measurements of mean or systolic \ac{abp} and \ac{nbp} at the same time for two consecutive times with the specified lags.
For the systolic measurements, 290, 332, and 442 points are available for the lags of one, five, and 15 minutes; for the mean measurements, 406, 430, and 542.

>>>>

During the COVID-19 pandemic, the need for reliable and timely nowcasts of the pandemic's development has become apparent.
In Germany, the seven-day hospitalization rate was established as a central steering measure for COVID-19 measures in November 2021, and the imposition of severe public restrictions was based on it~\parencite{RobertKochInstitute2021}.
The Robert Koch Institute (RKI) provides daily reports on the number of new hospitalizations.
However, these reports are subject to delays and revisions in two sources.
The first source is technical delays in the reporting process, for example, due to different authorities passing the data to the RKI~\parencite{RobertKochInstitute2024}.
The second, more systematic source is the structure of the seven-day hospitalization rate.
To a given date, all the cases are allocated whose first positive test result was on that date and who were hospitalized in relation to the disease in the following.
The seven-day hospitalization rate is the average count of cases per $100,000$ inhabitants on the given date and six days before.
Thus, the final seven-day hospitalization rate can only be reported with a significant delay of up to more than 70 days.
Nevertheless, as the seven-day hospitalization rate was considered a major indicator of the pandemic's development, many organizations and institutions started to issue nowcasts, including research teams and newspapers.
To collect nowcasts of the seven-day hospitalization rate by different nowcast groups, the COVID19-Nowcasting-Hub was established~\parencite{ChairOfEconometricsAndStatisticsAtKarlsruheInstituteOfTechnology2024}.
The nowcasts contain the seven-day hospitalization rate's predictive mean, median , and quantiles.
\unsure{median}
\begin{figure}
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics{plots/covid_nowcast/00_true_data.pdf}
    \caption{Realisations.}
    \label{fig:app-covid-true}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics{plots/covid_nowcast/00_nowcast_data.pdf}
    \caption{Same-day nowcasts}
    \label{fig:app-covid-nowcast}
        \end{subfigure}
    \caption{True and nowcast data of the seven-day-hospitalization in Germany from November 22, 2021, to April 29, 2022 \parencite{ChairOfEconometricsAndStatisticsAtKarlsruheInstituteOfTechnology2024}.
    The outliers in the RKI model of values above $10^8$ are removed before the following analysis.}
    \label{fig:app-covid-true-nowcast}
\end{figure}

The data contains eight nowcasts from scientific and public institutions, nowcast communities, and a newspaper, using different input variables, calendar data, and length of training data.
The model structures are diverse, including Bayesian models, generalized additive models, and parametric bootstrapping.
Table~\ref{tab:app-covid-models} in the appendix lists the different abbreviations and the model's overall structure.
Using the nowcasts, two ensemble methods are constructed using the ensembles' mean or for the large .
We denote them by ENS-MEAN and ENS-MED.
In line with the initial study design, we consider the period from November 22, 2021, to April 29, 2022, as the evaluation period.
In contrast to~\textcite{Wolffram2023}, we use the newest data available on the true values, not the data from August 8, 2022.
\unsure{Nochmal längere Evaluation?}
We do not expand on the models' performance on specific regions or age groups in Germany and the probabilistic nowcast assessment.
Figure~\ref{fig:app-covid-true-nowcast} displays the true and nowcast data for the evaluation period.
The time comprises the fourth wave's end in December 2021 and nearly the entire fifth wave of the pandemic in Germany, lasting until May 28, 2022~\parencite{Tolksdorf2022}.
Table~\ref{tab:app-covid-rmse} summarizes the point evaluation measures for the issued mean of the different models.
The models issue same-day nowcasts for nearly all 159 days of the evaluation period~\parencite[see][Tables A2, A3, and A4]{Wolffram2023}.
The best-performing models in terms of RMSE and MAE are the ILM and RKI models.
The ensemble methods perform worse than the best models regarding the mean location.
The performance of the models is diverse, with more than twice as high RMSE values for the worst models compared to the best models.
Note that the high values for the EPI model could be driven by an exceptionally far-off value at the end of the evaluation period.

@@

\unsure{Generell bei diesem Abschnitt: man liest hier eigentlich nur Beobachtungen, kann man auch daraus Schlüsse ziehen? Kann man results und discussion verschmelzen?}

@@

For some patients, the data includes \ac{abp} and \ac{nbp} measurements.
For an overview of blood pressure measurement methods, see \textcite{Saugel2014}.
While non-invasive blood pressure measurement methods are relatively gentle, they are less accurate than invasive methods.
For critical patients, changes in blood pressure can be crucial for the treatment.
Thus, trending assessment can be performed in addition to standard accuracy analysis~\parencite[see, e.g., ]{Mostafa2020}.
Thus, we assess the trending ability of the non-invasive blood pressure measurements compared to the invasive blood pressure measurements.
Of the 64,168 numerical data records in the database, 2,662 include at least one measurement of systolic \ac{abp} and \ac{nbp} and ... include at least measurements of \ac{abp} and \ac{nbp} at the same time.
\unsure{... include ...?}
The data records generally include measurements for one patient.
\unsure{irgendwie wird die Datenstruktur nicht ganz klar beschrieben. Habe ich hier Datensätze von verschiedenen Patienten und bei jeem Datensatz gibt es dann fehlende Punkte von ABP oder NBP?}

@@

Again, we exclude the 10\% of absolute differences in trending assessment.
\unsure{vielleicht genauer: we exclude the smallest 10 \% of the absolute differences in the trend assessment.}
The resulting four-quadrant plots of the mean and systolic blood pressure measurements for the different lags are shown in Figure~\ref{fig:app-mimic-4q}.
The number of points in the four-quadrant plot is smaller due to the restriction to data records with measurements of mean or systolic \ac{abp} and \ac{nbp} at the same time for two consecutive times with the specified lags.
For the systolic measurements, 290, 332, and 442 points are available for the lags of one, five, and 15 minutes; for the mean measurements, 406, 430, and 542.
